Computer Science House Constitution

### 2020-10-09 constitution.tex
Adding chairperson debate section

>>>>

\asubsection{Selection of the Chairperson}
	\item Each candidate for the position of Chairperson will be requested to appear in a debate with all other candidates for the position.
		A debate will be presented in front of House and will consist of questions generated by the House, but not given to the candidates before the debate.
	\item All other processes as described in \ref{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)} still apply in addition to the terms described above.
